Detecting Photo Manipulation using Reflections on Curved Surfaces

### 2014-02-04 paper/main.tex
added more picture analyses

The first step to all of the techniques is obtaining lines in the image that are parallel in three-dimensional scene space (or should be if the image is genuine). The first couple of techniques require hand-picking matching points between the original objects in the scene and their virtual (reflected) counterparts. Then, straight lines are drawn connecting these point pairs out to infinity. These lines, if drawn through the same planar mirror, must all intersect at a single vanishing point. If they don't intersect cleanly, or intersect at multiple vanishing points, the image can be assumed to be forged, as seen in Figure~\ref{planar-vanishing-point-forged}. Furthermore, the midpoints of the same lines, in three-dimensional scene space, must also plausibly appear to intersect the reflective surface, as in Figure~\ref{planar-midpoint-genuine}. Finally, as in Figure~\ref{center-of-projection-planar-genuine}, if there are orthogonal parallel lines in the image (for example, on the frame of a mirror), we can check if there is a consistent position for the center of projection, or point camera.

@@

\subsection{Reflective Sphere Geometry}
% figure: colinearity of radius and projection of incident ray

@@

\subsection{Circle Finding}
\subsection{Edge Detection}
rudimentary edge detection to assist picking points for the circles
limitation: edges are relatively easy to find in these test images- plain background

@@

\section{Conclusion}
\subsection{Results}
\subsubsection{Effects of Human Error}
\subsection{Future Work}

>>>>

The first step to all of the techniques is obtaining lines in the image that are parallel in three-dimensional scene space (or should be if the image is genuine). The first couple of techniques require hand-picking matching points between the original objects in the scene and their virtual (reflected) counterparts. Then, straight lines are drawn connecting these point pairs out to infinity. These lines, if drawn through the same planar mirror, must all intersect at a single vanishing point. If they don't intersect cleanly, or intersect at multiple vanishing points, the image can be assumed to be forged, as seen in Figure~\ref{planar-vanishing-point-forged}. Furthermore, the midpoints of the same lines in three-dimensional scene space must also plausibly appear to intersect the reflective surface, as in Figure~\ref{planar-midpoint-genuine}. Finally, as in Figure~\ref{center-of-projection-planar-genuine}, if there are orthogonal parallel lines in the image (for example, on the frame of a mirror), we can check if there is a consistent position for the center of projection, or point camera.

@@

\subsection{Reflective Sphere Geometry}
% figure: colinearity of radius and projection of incident ray
\begin{figure}
	\centering
    	\includegraphics[width=0.6\textwidth]{colinear-radius}
	\caption{Since the point $P$, the reflection point $B$, the camera $C$, and the normal $N$ are all coplanar, and $N$ is an extension of the radius of a sphere, then $PB$ and any radius must be coplanar.}
	\label{colinear-radius}
\end{figure}

\begin{figure}
	\centering
    	\includegraphics[width=0.6\textwidth]{colinear-radius-camera-view}
	\caption{A view of Figure~\ref{colinear-radius} from the point of view of the camera $C$.}
	\label{colinear-radius-camera-view}
\end{figure}

@@

\subsection{Circle Finding}
rudimentary edge detection to assist picking points for the circles
limitation: edges are relatively easy to find in these test images- plain background

@@

\section{Conclusion}
\subsection{Results}

\subsubsection{Effects of Human Error}
\subsection{Future Work}
